---
title: "combine_plots"
author: "Catarina Pien"
date: "3/4/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls(all=TRUE))
library(dplyr)
library(gpplot2)
library(lubridate)
library(Polychrome)
```

To combine: 
- Species comp (zoop + drift)
- Season/WY (zoop + drift + chla)
- Inundation time series (zoop + drift)
- CPUE by season, wy (zoop + drift + chla + biovolume)

```{r}
root <- "WY2017_WY2019/data_figures"

# Proportional plot
driftProp <- read_csv(here::here(root,"ProportionalData.csv")) %>%
  mutate(fWY = case_when(fWY == "2017" ~ "WY17",
                         fWY == "2018" ~ "WY18",
                         fWY == "2019" ~ "WY19",
                         TRUE ~ as.character(fWY)))
zoopProp <- read_csv(here::here(root, "zoop_percent.csv"))%>%
  rename(Station = Station.Code) %>%
  mutate(Org2 = ifelse(Org2 == "Acanthocyclops vernalis adult", "Acanthocyclops spp. adult", Org2))

# Bar plot station/WY
driftBar <- read_csv(here::here(root, "meanDriftBugs.csv"))%>%
  mutate(fWY = case_when(fWY == "2017" ~ "WY17",
                         fWY == "2018" ~ "WY18",
                         fWY == "2019" ~ "WY19",
                         TRUE ~ as.character(fWY)))
zoopBar <- read_csv(here::here(root, "zoop150.sum.csv"))%>%
  rename(Station = Station.Code)
chlBar <- read_csv(here::here(root, ".csv"))
phytoBar <- read_csv(here::here(root, ".csv"))

# Inundation Plot
inun <- read_csv(here::here(root, "inundation2.csv")) %>%
  mutate(inunD = ifelse(Inundation == "FALSE", 0, 175),
    inunZ = ifelse(Inundation == "FALSE", 0, 3e05))
driftInun <- read_csv(here::here(root, "driftDailyCPUE.csv"))
zoopInun <- read_csv(here::here(root, "zoop150.sum1.csv"))%>%
  rename(Station = Station.Code)
chlInun <- read_csv(here::here(root, ".csv"))
phytoInun <- read_csv(here::here(root, ".csv"))
  
```

```{r}
theme_ltreport <- theme_bw() + 
  theme(axis.text = element_text(size = 14),
                        axis.title = element_blank(),
                        strip.text = element_text(size = 13),
                        axis.text.x = element_text(angle = 90),
                        legend.title = element_text(size = 11),
                        legend.text = element_text(size = 9.5),
        legend.position = "top")
```

```{r}
pal36 <- palette36.colors(36)
pal36 <- as.vector(t(pal36))
```

## Make Proportional Plots

Pre-steps: for each, took total dataset, calculated the proportion of each taxa per station/year grouping. Any taxa that was <3% of that station/year's CPUE was classified as "other." All the "others" were combined into one percentage. 

### Drift
```{r}
# Proportional
(plot_driftProp <- ggplot(driftProp, aes(x=fWY, y = Percent/100, fill = Order3)) + 
   geom_bar(stat = "identity", color = "black") + facet_wrap(~Station) +
  scale_fill_manual(values = pal36) + 
  labs(title= "B) Drift Invertebrates", 
       y = "Proportional Catch Per Unit Effort", x = "Water Year") + 
   theme_ltreport + 
   theme(axis.text.x = element_text(angle = 45, vjust = 0.5), 
         legend.title = element_blank(),                                                      axis.title.y = element_blank()) +
    guides(fill=guide_legend(nrow=2)))

```

### Zoop
```{r}
zoopProp2 <- zoopProp %>%
  group_by(Station, WY, Org2) %>%
  summarize(totalPercent = sum(percent))
# This one
(plot_zoopProp <- ggplot(zoopProp2, aes(x=WY, y = totalPercent, fill = Org2)) + 
   geom_bar(stat = "identity", color = "black") + facet_wrap(~Station) +
  scale_fill_manual(values = pal36) + 
  labs(title= "A) Zooplankton", 
       y = "Proportional Catch Per Unit Effort", x = "Water Year") + 
   theme_ltreport + 
   theme(axis.text.x = element_text(angle = 45, vjust = 0.5), 
         legend.title = element_blank(),                                                      axis.title.y = element_blank())+
    guides(fill=guide_legend(nrow=3)))
```

### Combined
```{r}
library(ggpubr)
library(gridExtra)

(combined <- ggarrange(plot_zoopProp, plot_driftProp, nrow = 2))

annotated <- annotate_figure(combined, 
                left = text_grob("Proportional Catch Per Unit Effort", color = "black", rot = 90, size = 14))

annotated
```

```{r}
tiff(filename = paste("WY2017_WY2019/figures/fig_proportionalcombined.tiff"), res = 300, width = 8, height = 9, pointsize = 11, family = "sans", units = "in", compression = "lzw")
annotated
dev.off()
```


## Make WY/station bar plots

### Drift
```{r}
#Mean CPUE
(plot_barDrift <- ggplot(driftBar, aes(x = fWY, y = meanCPUE, fill = WYClass)) + 
   geom_col()  + 
   geom_errorbar(aes(ymin = meanCPUE-se, ymax = meanCPUE + se), width = .2) +
   labs(title = "B) Drift Invertebrates")+
 facet_wrap(~Station) + scale_fill_viridis(discrete = TRUE, option = "cividis", begin = 1, end = 0) + labs(x = "Water Year", y = expression(Mean~Daily~CPUE~(Count~m^-3))) +
  guides(fill = guide_legend(title = "Water Year Class")) + theme_ltreport + theme(legend.position = "top"))
```

### Zoop
```{r}
zoopBar2<- zoopBar %>% 
  group_by(Station, WY, WY.Class) %>% summarize(meanCPUE = mean(daily.CPUE, na.rm = TRUE),
            sdCPUE = sd(daily.CPUE, na.rm = TRUE),
            n = n(),
            se = sdCPUE/sqrt(n))


(plot_barZoop <- ggplot(zoopBar2, aes(x = WY, y = meanCPUE, fill = WY.Class)) + 
   geom_col()  + 
   geom_errorbar(aes(ymin = meanCPUE-se, ymax = meanCPUE + se), width = .2) +
    labs(title = "A) Zooplankton") +
 facet_wrap(~Station) + scale_fill_viridis(discrete = TRUE, option = "cividis", begin = 1, end = 0) + labs(x = "Water Year", y = expression(Mean~Daily~CPUE~(Count~m^-3))) +
  guides(fill = guide_legend(title = "Water Year Class")) + theme_ltreport + theme(legend.position = "top"))
```

### Chlorophyll
```{r}

```

### Combined
```{r}
library(ggpubr)
library(gridExtra)

(combinedBar <- ggarrange(plot_barZoop, plot_barDrift, nrow = 2, common.legend = TRUE))

annotatedBar <- annotate_figure(combinedBar, 
                left = text_grob(expression(Catch~Per~Unit~Effort~(Count~m^-3)), color = "black", rot = 90, size = 14))

annotatedBar
```

```{r}
tiff(filename = paste("WY2017_WY2019/figures/fig_barcombined.tiff"), res = 300, width = 8, height = 8, pointsize = 11, family = "sans", units = "in", compression = "lzw")
annotatedBar
dev.off()
```



## Make Inundation plots

### Drift
```{r}
color = c("lightblue", "white")
# Total CPUE
(plot_inunDrift <- ggplot() +
  geom_col(data = inun, aes(x = Date, y = inunD, fill = color, alpha = color)) +
  geom_line(data = driftDailyCPUE, aes(x = Date, y = CPUEDaily, linetype = Station, color = Station)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%Y") +
   scale_colour_manual(values = c("hotpink3", "black")) + 
    scale_alpha_manual(values = c(1, 0), guide = "none") +
  labs(title = "B) Drift Invertebrates", y = expression(CPUE~(Count~m^-3))) +
 scale_fill_manual(values = c("lightblue", "white")) +
    theme_bw() + 
  theme_ltreport + 
   theme(axis.title.x = element_blank(),
         legend.key=element_rect(colour="black")))
  #scale_fill_manual(name = "Inundation", values = c("light blue", "white"), guide = guide_legend(override.aes = list(color = c("light blue", "white")))))
```

### Zoop
```{r}
(plot_inunZoop <- ggplot() +
  geom_col(data = inun, aes(x = Date, y = inunZ, fill = color, alpha = color)) +
  geom_line(data = zoopInun, aes(x = Date, y = daily.CPUE, linetype = Station, color = Station)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%Y") +
   scale_colour_manual(values = c("hotpink3", "black")) + 
    scale_alpha_manual(values = c(1, 0), guide = "none") +
  labs(title = "A) Zooplankton", y = expression(CPUE~(Count~m^-3)), fill = "Inundation") +
 scale_fill_manual(values = c("lightblue", "white")) +
    theme_bw() + 
  theme_ltreport + 
   theme(axis.title.x = element_blank(),
         legend.key=element_rect(colour="black")))
```

### Chlorophyll
```{r}

```

### Combined
```{r}
library(ggpubr)
library(gridExtra)

(combinedInun <- ggarrange(plot_inunZoop, plot_inunDrift, nrow = 2, common.legend = TRUE))

annotatedInun <- annotate_figure(combinedInun, 
                left = text_grob(expression(Catch~Per~Unit~Effort~(Count~m^-3)), color = "black", rot = 90, size = 14))

annotatedInun
```

```{r}
tiff(filename = paste("WY2017_WY2019/figures/fig_inuncombined.tiff"), res = 300, width = 8, height = 8, pointsize = 11, family = "sans", units = "in", compression = "lzw")
annotatedInun
dev.off()
```


Grid arrange separate legend
```{r}
# save legend separately for final figure
get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

legend <- get_legend(plot)

# Annotate
plot21NR_avg3 <- annotate_figure(plot21NR_avg2, 
                left = text_grob("21°C", color = "black", rot = 90, size = 14))

# Plot
plotComb <- grid.arrange(legend, plot, plot2, plot3, 
                            nrow = 3,
            layout_matrix = rbind(c(1,1,2), c(3,4,5)), 
             widths = c(3.23,3,2.85), heights = c(0.75,3))
dev.off()
```

## Export code
```{r}
tiff(filename = paste("WY2016_WY2019/figures/fig_drift4b_totalcpuebyinundation.tiff"), res = 300, width = 7, height = 5, pointsize = 11, family = "sans", units = "in", compression = "lzw")
inunDriftAll
dev.off()
```

