---
title: "Model - LT Report"
author: "Parisa Farman"
output: html_document
editor_options: 
  chunk_output_type: console
---
###Step 1: Install packages 
```{r}

library(tidyverse)
library(readxl)
library(lubridate)
library(viridis)
library(dplyr)
library(scales)
library(ggthemes)
library(visreg)
library(tiff)
library(grid)
library(gridExtra)
library(here)
```

### Step 2: Set WD, read in data and restructure data to working data frame
```{r}
#setwd("X:\\YB_Manuscripts, Reports, Newsletters (AEU)\\YoloBypass_AnnualReport_LowerTrophic\\Lower Trophic Report_2017-2019\\Nutrients\\Data")
tiff
                              
#Filter out analytes of interest
physanalyte<-filter(phys,Analyte %in% c("DisAmmonia", "DisNitrateNitrite","DisSilica","DOP"))

#Remove labeled duplicates, remove irrelevant columns 
phys_normal <- physanalyte %>%
  filter(Purpose == "Normal Sample") %>%
  group_by(StationCode,Date,Time,Analyte) %>%
  slice(1) %>% select(-Units,-Method,-Depth)

#Removing duplicates that aren't labeled 
phys_normal %>% group_by (StationCode, Date, Analyte) %>% filter(duplicated(Result))

#Flip to wide format 
phys_wide<-phys_normal %>% pivot_wider(names_from="Analyte", values_from ="Result")

#Add in reporting limits for each analyte and condition by date, note that this step just creates new columns with the RL for each analyte 
phys_RL<-phys_wide %>% mutate(RL_DisAmmonia=ifelse(Date>="2018-11-27", 0.05, 0.01), RL_DisNitrateNitrite=ifelse(Date>="2018-11-27", 0.05, 0.01),
RL_DisSilica=0.1,RL_DOP=ifelse(Date>="2018-11-27", 0.05, 0.01)) 
```              

###Step 3: Create RL columns and create functions 
``` {r}
#Tell R which columns are RL and which are real value columns 
RL_columns<-grep('RL_*',colnames(phys_RL))

val_columns<-c(5:8)


#Define functions
zip <- function(...) { # based off Python zip
  mapply(list, ..., SIMPLIFY = FALSE)
}
#Mapply function is used to apply a function to multiple list or vector arguments. Simplify: attempt to reduce the result to a vector, matrix\ runs function on matrix, takes place of for loop, false returns a dataframe rather than a matrix which is what we want 
#It's important that our results have the same amount of significant figures 
sigfigs <- function(x){ # to determine # of sigfigs
  orig_scipen <- getOption("scipen")
  options(scipen = 999)
  on.exit(options(scipen = orig_scipen))

  x <- as.character(x)
  x <- sub("\\.", "", x)
  x <- gsub("(^0+|0+$)", "", x)
  nchar(x)
}
#this step is to conduct a uniform sample to insert real values into the <R.L. occurances 
samp_unif <- function(val_columns,RL_columns){ # the sampling function to go into lapply
  signif(runif(length(val_columns),0,RL_columns)[seq(val_columns)],digits = sigfigs(RL_columns))
}

```

### Step 4: Format data 
```{r}

#Needs to be NA so function can read it 

df=phys_RL %>% mutate(DisAmmonia=replace(DisAmmonia,DisAmmonia=="< R.L.",NA), DisNitrateNitrite=replace(DisNitrateNitrite,DisNitrateNitrite=="< R.L.",NA), DisSilica=replace(DisSilica, DisSilica=="< R.L.",NA), DOP=replace(DOP,DOP=="< R.L.",NA))

#Change results from characters to numeric values 

#str(df)
df$DisAmmonia <- as.numeric(as.character(df$DisAmmonia))
df$DisNitrateNitrite <- as.numeric(as.character(df$DisNitrateNitrite))
df$DisSilica <- as.numeric(as.character(df$DisSilica))
df$DOP <- as.numeric(as.character(df$DOP))
df$Date <- as.Date(df$Date)

#Get rid of WY 2020 values 

df <- filter(df, Date < "2019-10-1")

```
###Step 5: Prep for running models 

```{r}
#Use zip function to create a new data frame that can be used to run models 
df_zip <- zip(df[val_columns],df[RL_columns])

#Define priors for func, consider using n=10
models <- list()
n <- 10

#Define new dataframe which will use lapply to create a uniform distribution of values for <R.L. occurances 
for (n in seq(n)) {
  # add in random vals
  df_iter <- df
  df_iter[val_columns] <- lapply(df_zip, function(x) ifelse(is.na(x[[1]]), samp_unif(x[[1]],x[[2]]), x[[1]]))}
 
#check new data frame structure 
#str(df_iter)

```

###Step 6: Remove outliers (Outliers determined in Plot Code)

```{r}
df_iter$Index <- 1:nrow(df_iter)
df_iter <- df_iter %>% mutate(DisNitrateNitrite = replace(DisNitrateNitrite, Index==179, NA)) %>% mutate(DisNitrateNitrite = replace(DisNitrateNitrite, Index==204, NA)) %>% mutate(DisAmmonia =replace(DisAmmonia, Index==24, NA))
```

###Step 7: Run models on relationships between analytes that we're interested in, one is the predicting factor of the the other, so for aov(Analyte ~ Year, Dataframe) Year is a predicting factor of the analyte. In addition explore residuals - check for normal distribution, variation, can extract residuals from each model using function resid,  plot residuals against analyte in model (plot E against Dis NitrateNitrate etc), 

```{r}  
 #1 
  modelDNNDA <-lm(log(DisNitrateNitrite) ~ log(DisAmmonia), df_iter)
  summary(modelDNNDA)
  hist(log(df_iter$DisAmmonia))
  hist(log(df_iter$DisNitrateNitrite))
  par(mfrow = c(2,2)) 
  plot(modelDNNDA, add.smooth = FALSE)
  EDNNDA <- resid(modelDNNDA)
  hist(EDNNDA)
  #very significant, can indicate nitrification plays a role but still unclear

#in archive file, model between calcium and phosphorus 
  
#2
  modelDSDNN <- lm (log(DisSilica) ~ log(DisNitrateNitrite),   df_iter)
  summary(modelDSDNN)
  hist(log(df_iter$DisSilica))
  hist(log(df_iter$DisNitrateNitrite))
  par(mfrow = c(2,2)) 
  plot(modelDSDNN, add.smooth = FALSE)
  EDSDNN <- resid(modelDSDNN)
  hist(EDSDNN)
  #significant 
  
```

### Step 8: Create models for analytes vs WaterYear, check residuals 

```{r}
#create variable for year and month, water year = case_when(Month %in% c(10,11,12) ~ Year + 1, TRUE = year) need to add mutate function 
df_iter$Year <- year(df_iter$Date)
df_iter$Month <- factor(month(df_iter$Date))
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct", "Nov", "Dec")
#add abbreviated month name
df_iter$MonthAbb <- mymonths[df_iter$Month]
#set order of months
df_iter$MonthAbb <-ordered(df_iter$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

###breaking down year by water year   
df_iter$Month <- as.numeric(as.factor(df_iter$Month))
#str(df_iter)

df_iter_WY <- mutate(df_iter, WaterYear=case_when(Month %in% c(10,11,12) ~ Year+1, TRUE ~ Year))

df_iter_WY$WaterYear <- as.factor(df_iter_WY$WaterYear)
#str(df_iter_WY) ###make Year a factor 

WYModel1 <- aov(log(DisAmmonia) ~ WaterYear, df_iter_WY)
summary(WYModel1)

WYModel2 <- aov(log(DisNitrateNitrite) ~ WaterYear, df_iter_WY)
summary(WYModel2)

WYModel3 <- aov(log(DisSilica) ~ WaterYear, df_iter_WY)
summary(WYModel3)

WYModel4 <- aov(log(DOP) ~ WaterYear, df_iter_WY)
summary(WYModel4)

####None of these are significant, water year does not impact analytes 
### Changed this to factor and now they are all significant
```

###Step 9: Look at how chlorophyll and nutrients are related 

```{r}
chla_data <- read_excel(path="LT_discrete_chla_RAW_2022_PF.xlsx")
chla_data$Date <- as.Date(chla_data$Date)
chla_data$Result <- as.numeric(chla_data$Result)
str(chla_data)

chla_data_filtered <- chla_data %>% filter(Analyte=="Chla") %>% select(-Units,-Method,-Depth) %>% group_by(Date, StationCode) %>% dplyr::summarize(Result = mean(Result)) %>% filter (Date < "2019-10-01")


chla_nutrients <- merge(x=df_iter,              
              y=chla_data_filtered,
              by= c('StationCode','Date'),
              all=TRUE)

modelchDA <-lm(log(Result) ~ log(DisAmmonia), chla_nutrients)
  summary(modelchDA)
  ##significant p value = 0.312
  #hist(chla_nutrients$Result)
  #hist(log(chla_nutrients$Result))
  par(mfrow = c(2,2)) 
  plot(modelchDA, add.smooth = FALSE)
  EchDA <- resid(modelchDA)
  hist(EchDA)
  
modelDNNch <-lm(log(Result) ~ log(DisNitrateNitrite), chla_nutrients)
  summary(modelDNNch)
  par(mfrow = c(2,2)) 
  plot(modelDNNch, add.smooth = FALSE)
  EDNNch <- resid(modelDNNch)
  hist(EDNNch)  
  
modelDSch <-lm(log(Result) ~ log(DisSilica), chla_nutrients)
  summary(modelDSch)
  ##not significant 
  
modelDOPch <-lm(log(Result) ~ log(DOP), chla_nutrients)
  summary(modelDOPch)
  par(mfrow = c(2,2)) 
  plot(modelDOPch, add.smooth = FALSE)
  EDOPch <- resid(modelDOPch)
  hist(EDOPch) 
  #significant
```

###Step 10.1: Consider how seasons affect nutrient concentrations do over, original in archive code 
```{r}
df_iter_seasons <- df_iter_WY %>% mutate(Seasons = ifelse(MonthAbb %in% c("Jan", "Feb", "Mar"), "Winter", ifelse(MonthAbb %in% c("Apr", "May", "Jun"), "Spring", ifelse(MonthAbb %in% c("Jul", "Aug", "Sep"), "Summer", ifelse(MonthAbb %in% c("Oct", "Nov", "Dec"), "Fall", NA)))))

df_iter_seasons$StationCode <- factor(df_iter_seasons$StationCode, levels = c("LIS", "STTD", "SHR"))

SeasonDA <- aov(log(DisAmmonia) ~ Seasons*StationCode, df_iter_seasons)
summary(SeasonDA)
##Season not significant, site significant 
TukeySeasonDA <- TukeyHSD(x=SeasonDA)
visreg(SeasonDA,"StationCode")

SeasonDNN <- aov(log(DisNitrateNitrite) ~ Seasons*StationCode, df_iter_seasons)
summary(SeasonDNN)
#All significant 
#Run Tukey test 
TUKEYSeasonDNN <- TukeyHSD(x=SeasonDNN)
visreg(SeasonDNN,"StationCode")
visreg(SeasonDNN,"Seasons")
visreg(SeasonDNN,"StationCode", by="Seasons")
visreg(SeasonDNN,"Seasons", by="StationCode")


SeasonDS <- aov(log(DisSilica) ~ Seasons*StationCode, df_iter_seasons)
summary(SeasonDS)
TUKEYSeasonDS <- TukeyHSD(x=SeasonDS)
visreg(SeasonDS,"StationCode")
visreg(SeasonDS,"Seasons")
visreg(SeasonDS,"StationCode", by="Seasons")
visreg(SeasonDS,"Seasons", by="StationCode")

SeasonDOP <- aov(log(DOP) ~ Seasons*StationCode, df_iter_seasons)
summary(SeasonDOP)
TUKEYSeasonDOP <- TukeyHSD(x=SeasonDOP)
visreg(SeasonDOP,"StationCode")
visreg(SeasonDOP,"Seasons")
visreg(SeasonDOP,"StationCode", by="Seasons")
visreg(SeasonDOP,"Seasons", by="StationCode")
```

```{r}
# Cat redo models with WY
# Dissolved Ammonia
ModelDA1 <- aov(log(DisAmmonia) ~ Seasons + StationCode + WaterYear, df_iter_seasons)
summary(ModelDA1)
ModelDA2 <- aov(log(DisAmmonia) ~ StationCode + WaterYear, df_iter_seasons)
summary(ModelDA2)
anova(ModelDA2)
ModelDA3 <- aov(log(DisAmmonia) ~ StationCode + WaterYear + StationCode:WaterYear, df_iter_seasons)
summary(ModelDA3)

AIC(ModelDA1, ModelDA2, ModelDA3)
plot(ModelDA2)
TukeyHSD(x=ModelDA2)
visreg(ModelDA2)

# DissolvedNN

ModelDNN1 <- aov(log(DisNitrateNitrite) ~ Seasons + StationCode + WaterYear, df_iter_seasons)
summary(ModelDNN1)
ModelDNN2 <- aov(log(DisNitrateNitrite) ~ Seasons*StationCode + WaterYear, df_iter_seasons)
summary(ModelDNN2)
anova(ModelDNN2)
ModelDNN3 <- aov(log(DisNitrateNitrite) ~ Seasons*StationCode + Seasons*WaterYear, df_iter_seasons)
summary(ModelDNN3)

AIC(ModelDNN1, ModelDNN2, ModelDNN3)
par(mfrow = c(2,2))
plot(ModelDNN2)
TukeyHSD(x=ModelDNN2)
anova(ModelDNN2)
visreg(ModelDNN2)
visreg(ModelDNN2, "StationCode", by= "WaterYear")
visreg(ModelDNN2, "StationCode", by= "Seasons")
visreg(ModelDNN2, "WaterYear", by= "Seasons")

# DS
ModelDS1 <- aov(log(DisSilica) ~ Seasons + StationCode + WaterYear, df_iter_seasons)
summary(ModelDS1)
ModelDS2 <- aov(log(DisSilica) ~ StationCode + WaterYear, df_iter_seasons)
summary(ModelDS2)
anova(ModelDS2)
ModelDS3 <- aov(log(DisSilica) ~ StationCode + WaterYear + StationCode:WaterYear, df_iter_seasons)
summary(ModelDS3)

AIC(ModelDS1, ModelDS2, ModelDS3)
par(mfrow = c(2,2))
plot(ModelDS3)
TukeyHSD(x=ModelDS3)
anova(ModelDS3)
visreg(ModelDS3)
visreg(ModelDS3, "StationCode", by = "WaterYear")

# DOP
ModelDOP1 <- aov(log(DOP) ~ Seasons + StationCode + WaterYear, df_iter_seasons)
summary(ModelDOP1)
ModelDOP2 <- aov(log(DOP) ~ StationCode + Seasons*WaterYear, df_iter_seasons)
summary(ModelDOP2)
anova(ModelDOP2)

AIC(ModelDOP1, ModelDOP2)
par(mfrow = c(2,2))
plot(ModelDOP2)
anova(ModelDOP2)
TukeyHSD(x=ModelDOP2)
visreg(ModelDOP2)
visreg(ModelDOP2, "Seasons", by = "WaterYear")
```





###Step 11: Consider how inundation periods affect nutrient concentrations 
```{r}
inundation_data <- read_excel(here(root, "InundationWY2010toWY2019.xlsx"))
str(inundation_data)
inundation_data$Date <- as.Date(inundation_data$Date)
inundation_data_WYS <- inundation_data %>% 
  filter(Date >= "2016-10-01", Date <= "2019-09-30") %>% 
  subset(select=-c(2:5))

Inun_nutrients <- merge(x=df_iter_WY,              
              y=inundation_data_WYS,
              by= "Date",
              all=FALSE)

###take off sherwood 
Inun_nutrients_Yolo<-filter(Inun_nutrients, StationCode !="SHR") 
str(Inun_nutrients_Yolo)
Inun_nutrients_Yolo$Inundation = as.factor(Inun_nutrients_Yolo$Inundation)

##Run models 
MInunDA <- aov(log(DisAmmonia) ~ Inundation, Inun_nutrients_Yolo)
summary(MInunDA)
#not significant 

MInunDNN <- aov(log(DisNitrateNitrite) ~ Inundation, Inun_nutrients_Yolo)
summary(MInunDNN)
#not significant 

MInunDS <- aov(log(DisSilica) ~ Inundation, Inun_nutrients_Yolo)
summary(MInunDS)
TUKEYInunDS <- TukeyHSD(x=MInunDS)
##significant 
visreg(MInunDS,"Inundation")

MInunDOP <- aov(log(DOP) ~ Inundation, Inun_nutrients_Yolo)
summary(MInunDOP)
##significant 
TUKEYInunDOP <- TukeyHSD(x=MInunDOP)
visreg(MInunDOP,"Inundation")


MInunDOPt <- aov(Inun_nutrients_Yolo$log(DOP), Inun_nutrients_yolo$Inundation)
summary(MInunDOP)
```

###Step 12: Consider how inundation periods affect chlorophyll concentrations 
```{r}

Inun_Chla <- merge(x=chla_data_filtered,              
              y=inundation_data_WYS,
              by= "Date",
              all=FALSE)

###take off sherwood 
Inun_Chla_Yolo<-filter(Inun_Chla, StationCode !="SHR") 

##Run models 
MInun_Chla <- aov(log(Result) ~ Inundation, Inun_Chla_Yolo)
summary(MInun_Chla)
# significant 

```

###Step 13: Consider how seasons affect chlorophyll concentrations 
```{r}

## need to merge Chla data with dfiterseasons 

chla_seasons <- merge(x=df_iter_seasons,              
              y=chla_data_filtered,
              by= c('StationCode','Date'),
              all=TRUE)

#Restructing data so that new chla values have an associated season 
chla_seasons$Year <- year(chla_seasons$Date)
chla_seasons$Month <- factor(month(chla_seasons$Date))
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct", "Nov", "Dec")

#add abbreviated month name
chla_seasons$MonthAbb <- mymonths[chla_seasons$Month ]
#set order of months
chla_seasons$MonthAbb <-ordered(chla_seasons$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

chla_seasons <- chla_seasons %>% mutate(Seasons = ifelse(MonthAbb %in% c("Jan", "Feb", "Mar"), "Winter", ifelse(MonthAbb %in% c("Apr", "May", "Jun"), "Spring", ifelse(MonthAbb %in% c("Jul", "Aug", "Sep"), "Summer", ifelse(MonthAbb %in% c("Oct", "Nov", "Dec"), "Fall", NA)))))
 

## All sites together 
MChla_Seasons <- aov(log(Result) ~ Seasons*StationCode, chla_seasons)
summary(MChla_Seasons)
#allsignificant 
#posthoc test 
TUKEYChla <- TukeyHSD(x=MChla_Seasons)
visreg(MChla_Seasons,"StationCode", ylab= "log (Chlorophyll)")
visreg(MChla_Seasons,"Seasons", ylab= "log (Chlorophyll)")
visreg(MChla_Seasons,"StationCode", by="Seasons")
visreg(MChla_Seasons,"Seasons", by="StationCode")

```

###Step 14: Make Cholorophyll graph 
```{r}

chla_data_filtered <- filter(chla_data_filtered, !StationCode=="NA")
chla_data_filtered$StationCode <- factor(chla_data_filtered$StationCode, levels = c("LIS", "STTD", "SHR"))

(pChlorophyll <- ggplot() +
        geom_line(chla_data_filtered, mapping = aes(Date, Result, group = StationCode, colour = StationCode), na.rm = TRUE,  size = 1.1) +
        geom_point(chla_data_filtered, mapping = aes(Date, Result, group = StationCode, colour = StationCode, shape = StationCode), na.rm = TRUE, size = 3) +
   scale_x_date(date_breaks = "3 months", date_labels = "%b-%Y") + 
  labs(title = "Chlorophyll-a vs Time", y="Chlorophyll-a (µg/L)", size = 12) + 
  theme_bw() + scale_color_viridis(discrete=TRUE, direction = -1) +
  theme(axis.text.x=element_text(angle=90, size=12), axis.title.x=element_blank()) +
  theme(axis.text.y=element_text(size=12)))

#Export graph 
tiff(filename = "Chlorophyll.tiff", res = 300, width = 15, height = 7, pointsize = 11, family = "sans", units = "in", compression = "lzw") 
(grid.arrange(pChlorophyll)) 
dev.off() 

```
